### 2014-05-21 acks.tex
Add Roger

Thank you to the subscribers of MIT Zephyr's help class, who
organized themselves at the last minute to proofread this
dissertation for me: Laura Baldwin, Jacob Morzinski, Mark Eichin, Carl
``Alex'' Alexander, Ben Kaduk, and Richard Tibbetts.

>>>>

Thank you to the subscribers of MIT Zephyr, who
organized themselves at the last minute to proofread this
dissertation for me: Roger Ford, Laura Baldwin, Jacob Morzinski, Mark Eichin, Carl
``Alex'' Alexander, Ben Kaduk, and Richard Tibbetts.
